---
title: 'Programming Assignment 2: Lexical Scoping'
author: "Jerez"
date: "11/17/2020"
output: html_document
---

## Assignment: Caching the Inverse of a Matrix

Matrix inversion is usually a costly computation and there may be some benefit to caching the inverse of a matrix rather than compute it repeatedly (there are also alternatives to matrix inversion that we will not discuss here). Your assignment is to write a pair of functions that cache the inverse of a matrix.

Write the following functions:

1. *makeCacheMatrix*: This function creates a special "matrix" object that can cache its inverse.

2. *cacheSolve*: This function computes the inverse of the special "matrix" returned by *makeCacheMatrix* above. If the inverse has already been calculated (and the matrix has not changed), then the *cachesolve* should retrieve the inverse from the cache.

Computing the inverse of a square matrix can be done with the solve function in R. For example, if X is a square invertible matrix, then solve(X) returns its inverse.

## Solution

The function that we must create, must contain spaces to establish and to obtain the values of the matrix and its inverse. 

```{r}
makeCacheMatrix <- function(x = matrix()) {
    inv <- NULL           # Initialize the inverse property
    
    set <- function(matrix) {  # Function to set the matrix 
        x   <<- matrix
        inv <<- NULL}
    get <- function() x        # Return the matrix
    
    setinverse <- function(inverse) # Function to set inverse of the matrix
    inv <<- inverse
    getinverse <- function() inv    # Return the inverse
    
    # Outputs
    list(set=set, get=get, setinverse=setinverse, getinverse=getinverse)
}
````

Now, *catchSolve*:

```{r}

cacheSolve <- function(s, ...) {
    inverse <- s$getInverse() # Return a matrix that is the inverse of 'x'

    if( !is.null(inverse)) { # Just return the inverse if its already set
            message("Getting cached data")
            return(inverse)
    }
    
    data    <- s$get()              # Get the matrix from our object
    inverse <- solve(data) %*% data # Inverse using matrix multiplication
    s$setInverse(x)                 # Set the inverse to the object 
    inverse                         # Return the matrix
}
````
